Sample-Based Determination of Angular Observables

### 2014-06-24 draft.tex
More corrections and comments, mostly on statistics and notation

%% Shortcuts %%
\newcommand{\dd}{\text{d}}
\newcommand{\refapp}[1]{app.~(\ref{app:#1})}
\newcommand{\refeq}[1]{eq.~(\ref{eq:#1})}
\newcommand{\refsec}[1]{sec.~(\ref{sec:#1})}
\newcommand{\reftab}[1]{tab.~(\ref{tab:#1})}
\newcommand{\nuvec}{\vec{\nu}}
\newcommand{\thvec}{\vec{\vartheta}}
\let\oldtheta\theta
\renewcommand{\theta}{\vartheta}
\newcommand{\GeV}{\text{GeV}}
\newcommand{\order}[1]{\mathcal{O}\left({#1}\right)}
\let\eps\varepsilon
\newcommand{\what}[1]{\widehat{#1}}
\newcommand{\wwhat}[1]{\widehat{\widehat{#1}}}
\DeclareMathOperator{\cov}{Cov}

@@

Let $\thvec = (\theta_1, \dots \theta_n)$ denote the set of all
angles, and let $\nuvec = (\nu_1, \dots \nu_m)$ denote the set of all
other non-angular kinematic variables needed to fully specify the
final state of the process under study. For example, $\nuvec$ may
include invariant masses or center-of-mass energies. We define an
angular observable $P_i$ as a coefficient in the probability density
function (PDF) of the process,
\begin{align}
    \label{eq:def-P}
    P(\nuvec, \thvec) = \sum_i P_i(\nuvec) \times f_i(\thvec)\,,
\end{align}
Here, the dependence on the $n$ decay angles $\thvec$ has been
explicitly factored out in terms of the angular functions
$f_i(\thvec)$, which we assume to fulfill the orthonormality relations
\begin{equation}
    \label{eq:def-ortho-rel}
    \int_\Omega f_i(\thvec) f_j(\thvec) \dd^n \theta = \delta_{ij}\,.
\end{equation}
(For the purpose of this letter, however, it suffices that the system
of angular functions $f_i(\thvec)$ can be transformed into an
orthonormal basis. The transformation needs to be worked out on a
case-by-case basis. For a selection of $B$ decays, the transformations
are listed in the appendices \ref{app:btokll} through
\ref{app:lambdabtolambdall}.)\\

For particle decays, $P$ is generally expressed in terms of the fully differential decay width,
\begin{align}
    \label{eq:def-P-decay}
    P(\nuvec, \thvec) \equiv \frac{1}{\Gamma}\frac{\dd^{n+m}\Gamma}{\dd \nu_1 \dots \dd \nu_m\, \dd \theta_1 \dots \theta_n}\,,
\end{align}
where $\Gamma$ is the total decay width. For a scattering process, one can similarly use
\begin{align}
    \label{eq:def-P-scattering}
    P(\nuvec, \thvec) \equiv \frac{1}{\sigma}\frac{\dd^{n+m}\sigma}{\dd \nu_1 \dots \dd \nu_m\, \dd \theta_1 \dots \theta_n}\,,
\end{align}
where the total cross section $\sigma$ is used for the normalisation. Since the determination of
the total decay width or total cross section can be quite difficult, we emphasize that different normalizations for
$P$ can be used. For instance, the total decay width (or cross section) of the process of interest can be replaced
by the corresponding quantity of a control-channel process.\\

In the remainder of this letter we discuss how to obtain the angular observables $P_i(\nuvec)$ in an experimental
setup where each recorded event is (approximately) as variate of $P$.
We lay down the groundwork in section \ref{sec:sample-based-det}. Section \ref{sec:systematics} is dedicated to
the impact of systematic effects, such as mismodelling of the underlying physics and detector acceptance
effects. Numerical studies for one uni-angular and one triple-angular distribution are provided in section
\ref{sec:numerics}. In a series of appendices we discuss the relevant orthonormal bases of angular functions
at the hand of the several rare $b$ decays.

@@

From the orthonormality relations \refeq{def-ortho-rel} follows that a single angular observable $P_i$
can be projected out of the full PDF $P$ by means of
\begin{equation}
    \label{eq:det-Pi-analytical}
    P_i(\nuvec) = \int_{\thvec = 0}^{2\pi} f_i(\thvec) P(\nuvec, \thvec) \dd^n \theta\,.
\end{equation}
In point of fact, $P_i$ is the $f_i$-moment of the PDF $P$. Additionally, Integration over the non-angular variables yields
\begin{equation}
    \langle P_i\rangle
    \equiv \int P_i(\nuvec) \dd^m \nu
    = \int \left[\int_{\thvec=0}^{2\pi} f_i(\thvec) P(\nuvec,\thvec) \dd^n\theta\right]\dd^m \nu\,.
\end{equation}
The remainder of this section is describes the method of moments, in which we replace the
analytical integration \refeq{det-Pi-analytical} by Monte Carlo (MC) estimators.\\

The central tenet of MC integration is the fact that the expectation value $E_P[g]$ of some function
$g(x)$ under the probability density $P(x)$,
\begin{equation}
    E_P[g] \equiv \int g(x) P(x) \dd x
\end{equation}
can be replaced \citeneeded by an MC estimator $\what{E_P[g]}$
\begin{equation}
    \label{eq:mc-id}
    E_P[g] \to \widehat{E_P[g]} \equiv \frac{1}{N} \sum_{k=1} g(x^{(k)})\,.
\end{equation}
For the purpose of the estimation, the variates $x^{(k)}$, $k = 1, \dots, N$ must distributed under $P$,
\begin{equation}
    x^{(k)} \sim P\,.
\end{equation}
(Throughout this letter we denote all MC estimators with a wide hat.)\\

We assume, for a moment, that $P$ describes the distribution of the underlying
physical process truthfully. In that case, all events detected in an experimental setup are in fact, up to
detection efficiencies, distributed as $P$. Application of \refeq{mc-id} then yields
\begin{equation}
    \langle P_i\rangle \to \widehat{\langle P_i\rangle} = \frac{1}{N} \sum_{k=1}^{N} f_i(x^{(k)})\,.
\end{equation}
However, it is often of interest to obtain the $\nuvec$-integrated observables for
certain $\nuvec$ ranges, i.e. binned measurements of $\langle P_i\rangle$\footnote{%
We refer for example to the determination of the angular observables $J_i$ in $\bar{B}\to\bar{K}^*\ell^+\ell^-$
decays, see e.g. \cite{Aaij:2013iag}. For details on the relation between the $P_i$ and the angular observable $J_i$ in the
aforementioned decay, we refer to appendix \ref{app:btokstarll}.
}.
Therefore, we introduce the bin-integrated quantities
\begin{align}
    \langle P_i\rangle_{\vec{a},\vec{b}}
    & = \int_{\vec{a}}^{\vec{b}} P_i(\nuvec) \dd^m \nu\\
    & = \int_{\vec{a}}^{\vec{b}} \left[\int_{\thvec=0}^{2\pi} f_i(\thvec) P(\nuvec,\thvec) \dd^n\theta\right]\dd^m \nu\\
    & = \int \left[\int_{\thvec=0}^{2\pi} f_i(\thvec) P(\nuvec,\thvec)
        \theta^{(m)}(\nuvec - \vec{a}) \theta^{(m)}(\vec{b} - \nuvec) \dd^n\theta\right]\dd^m \nu\,.
\end{align}
Application of \refeq{mc-id} immediately yields
\begin{equation}
    \widehat{\langle P_i\rangle_{\vec{a},\vec{b}}}
    = \frac{1}{N} \sum_{k=1}^{N} f_i(x^{(k)}) \theta^{(m)}(\nuvec^{(k)} - \vec{a}) \theta^{(m)}(\vec{b} - \nuvec^{(k)})\,.
\end{equation}
This basically reduces the determination of $P_i$ to a (weighted) counting experiment. As a consequence,
the statistical error on $\what{P_i}$ can be expected to follow a multivariate gaussian distribution \citeneeded.
In this case, the covariance $\cov[\what{P_i},\what{P_j}]$ is of particular interest. The latter can be replaced
by a suitable MC estimator, the sample covariance
\begin{equation}
    \cov[\what{P}_i,\what{P}_j] \to \what{\cov}[\what{P}_i, \what{P}_j]_{\vec{a},\vec{b}}
        = \frac{1}{N - 1} \sum_{k=1}^{N} \big[\hat{f}_i^{(k)} - \widehat{\langle P_i\rangle_{\vec{a},\vec{b}}}\big]\,\big[\hat{f}_j^{(k)} - \widehat{\langle P_j\rangle_{\vec{a},\vec{b}}}\big]
        \theta^{(m)}(\nuvec^{(k)} - \vec{a}) \theta^{(m)}(\vec{b} - \nuvec^{(k)})\,.
\end{equation}
We would like to emphasize that the sample covariance should rapidly converge towards the true covariance matrix.
This will allow to construct constraints on optimized observables with correlated uncertainties
from the experimental constraints on the angular observables. (See \cite{Egede:2008uy,Egede:2010zc,Bobeth:2010wg,Becirevic:2011bp,Bobeth:2012vn,Matias:2012xw,DescotesGenon:2012zf}
for definitions of such optimized observables in $B\to K^*\ell^+\ell^-$ decays).

@@

In \refsec{sample-based-det}, we assumed that the PDF $P$ described the physical reality accurately,
and that the experiment observed each event with perfect accuracy. In order to estimate systematic
uncertainties, we lift these assumptions.

\subsection{Mismodelling due to Contributions by Higher Partial Waves}
\label{sec:systematics:partial-waves}

@@

Thanks to accurate detector simulations and control studies, the experimental analyses have become
remarkably good at removing detector acceptance effects. In this section we therefore assume that
there are only a small, residual acceptance effects left that affect the events. In particular, we
assume that the latter can be modelled as a modified probability density,
\begin{equation}
    \label{eq:PDFwithDE}
    P(\nuvec,\thvec) \to P(\nuvec,\thvec) \times \Omega(\thvec),
\end{equation}
where $\Omega$ is independent of the non-angular kinematics $\nuvec$. The latter assumption is only
is invalid in general. However, if residual angular acceptance only weakly depends on $\vec{\nu}$, one
can always choose appropriate bin $\vec{\nu}$ so that $\Omega$ is approximately constant with respect
to $\vec{\nu}$. For such a case we parametrize
\begin{equation}
    \Omega_{m,l}(\thvec) = \prod_{i=1}^{m} \Big[1 + \sum_{j=1}^l \eps_i^{(j)} p_j(\cos\theta_i)\big]
\end{equation}
where $p_j(\cos\theta_i)$ denotes the $j$th Legendre polynomial. Since we only consider residual
acceptance effects, we expect $\eps_i^{(j)} \ll 1$. \footnote{\danny{what are reasonable values/upper limits on the $\eps$?}}\\

@@

\todo{
\begin{itemize}
    \item Simulate this for one angle $\theta_{1}$ (similar to $B\to K \ell^+\ell^-$) with varying samples sizes.
    \item Simulate this for three angles $\theta_{1\dots 3}$ (similar to $B\to K^*(\to K \pi)\ell^+\ell^-$) with varying samples sizes.
    \item Also, check explicitly the variance and covariance of the results for all sample sizes considered.
\end{itemize}}

@@

In this letter \dots
\begin{enumerate}
    \item errors on the means are in very good approximation gaussian.
    \item correlation are small and faithfully model a multivariate gaussian.
\end{enumerate}

@@

The PDF for the decay $\bar{B}\to\bar{K}\ell^+\ell^-$ has been calculated for the most
complete basis of dimension-six $b\to s \ell^+\ell^-$ operators. It reads \cite{Bobeth:2007dw,Bobeth:2012vn}
\begin{equation}
    P(q^2, \cos\theta_1) = \frac{1}{\Gamma} \frac{\dd^4\Gamma}{\dd q^2\,\dd \cos\theta_1} = \frac{a(q^2)}{\Gamma} + \frac{b(q^2)}{\Gamma} \cos\theta_1 + \frac{c(q^2)}{\Gamma} \cos^2\theta_1 = \sum_i P_i f_i(\cos\theta_1)\,,
\end{equation}
where the basis of angular functions $f_i$ reads
\begin{equation}
\begin{aligned}
    f_1 & = 1\,, &
    f_2 & = \cos\theta_1\,, &
    f_2 & = \cos^2\theta_1\,.
\end{aligned}
\end{equation}
Here we denote the dilepton mass squared as $q^2$, and the dilepton helicity angle as $\theta_1 \equiv \theta_{\ell}$. We transform the PDF from a $\cos\theta_1$-dependence
to a $\theta_1$-dependence,
\begin{equation}
    P(q^2, \theta_1) = \sum_i P_i f_i(\cos\theta_1) \sin \theta_1\,.
\end{equation}

We provide dual basis $\hat{f}_i$ of angular functions which is dual to the basis $f_i$ in the sence that
\begin{equation}
    \int_0^\pi \dd\theta_1 \hat{f}_i(\theta_1) f_j(\theta_1) \sin\theta_1 = \delta_{ij}\,,
\end{equation}
thereby enabling us to project out exactly one of the angular
observables $P_i(q^2)$
\begin{equation}
    \int_0^\pi \dd \theta_1\hat{f}_i(\theta_1) P(q^2, \theta_1) = P_i(q^2)\,.
\end{equation}
The dual basis reads
\begin{equation}
\begin{aligned}
    \hat{f}_1 & = \frac{9}{8} - \frac{15}{8}\cos^2\theta_1\,, &
    \hat{f}_2 & = \frac{3}{2}\cos\theta_1\,, &
    \hat{f}_3 & = -\frac{15}{8} + \frac{45}{8}\cos^2\theta_1\,.
\end{aligned}
\end{equation}

>>>>

%% Shortcuts %%
\newcommand{\dd}{\text{d}}
\newcommand{\refapp}[1]{app.~(\ref{app:#1})}
\newcommand{\refeq}[1]{eq.~(\ref{eq:#1})}
\newcommand{\refsec}[1]{sec.~(\ref{sec:#1})}
\newcommand{\reftab}[1]{tab.~(\ref{tab:#1})}
\newcommand{\nuvec}{\vec{\nu}}
\newcommand{\thvec}{\vec{\vartheta}}
\let\oldtheta\theta
\renewcommand{\theta}{\vartheta}
\newcommand{\GeV}{\text{GeV}}
\newcommand{\order}[1]{\mathcal{O}\left({#1}\right)}
\let\eps\varepsilon
\newcommand{\aver}[1]{\langle #1 \rangle}
\newcommand{\what}[1]{\widehat{#1}}
\newcommand{\wwhat}[1]{\widehat{\widehat{#1}}}
\DeclareMathOperator{\cov}{Cov}

@@

Let $\thvec = (\theta_1, \dots \theta_n)$ denote the set of all
angles, and let $\nuvec = (\nu_1, \dots \nu_m)$ denote the set of all
other non-angular kinematic variables needed to fully specify the
final state of the process under study. For example, $\nuvec$ may
include invariant masses or center-of-mass energies. We define an
angular observable $P_i$ as a coefficient in the probability density
function (PDF) of the process,
\begin{align}
    \label{eq:def-P}
    P(\nuvec, \thvec) = \sum_i P_i(\nuvec) \times f_i(\thvec)\,.
\end{align}
Here, the dependence on the $n$ decay angles $\thvec$ has been
explicitly factored out in terms of the angular functions
$f_i(\thvec)$, which we assume to fulfill the orthonormality relations
\begin{equation}
    \label{eq:def-ortho-rel}
    \int_\Omega f_i(\thvec) f_j(\thvec) \dd^n \theta = \delta_{ij}\,.
\end{equation}
For the purpose of this letter, however, it suffices that the system
of angular functions $f_i(\thvec)$ can be transformed into an
orthonormal basis. The transformation needs to be worked out on a
case-by-case basis. For a selection of $B$ decays, the transformations
are listed in the appendices \ref{app:btokll} through
\ref{app:lambdabtolambdall}.  Note that $P_i$ is \emph{not} a PDF.  \\

For particle decays, $P$ is generally expressed in terms of the fully differential decay width,
\begin{align}
    \label{eq:def-P-decay}
    P(\nuvec, \thvec) \equiv \frac{1}{\Gamma}\frac{\dd^{n+m}\Gamma}{\dd \nu_1 \dots \dd \nu_m\, \dd \theta_1 \dots \theta_n}\,,
\end{align}
where $\Gamma$ is the total decay width. For a scattering process, one can similarly use
\begin{align}
    \label{eq:def-P-scattering}
    P(\nuvec, \thvec) \equiv \frac{1}{\sigma}\frac{\dd^{n+m}\sigma}{\dd \nu_1 \dots \dd \nu_m\, \dd \theta_1 \dots \theta_n}\,,
\end{align}
where the total cross section $\sigma$ is used for the
normalization. Since the determination of the total decay width or
total cross section can be quite difficult, we emphasize that
different normalizations for $P$ can be used.  For instance, the total
decay width (or cross section) of the process of interest can be
replaced by the corresponding quantity of a control-channel
process.\fred{How would $P$ remain a proper probability such that
  $\int P = 1$? You can't simply change the normalization. I propose a
  change of notation: I find it terribly confusing that $P(\nuvec,
  \thvec)$ is a probability but $P_i(\nuvec)$ is not. For $P_i$, later
  on the symbols $J_i, K_i$ etc are used. We don't have to use the
  same symbol everywhere but let's not use $P_i$}\\

In the remainder of this letter we discuss how to obtain the angular
observables $P_i(\nuvec)$ in an experimental setup where each recorded
event is (approximately) distributed according to $P$.  We establish
the statistical basics in section \ref{sec:sample-based-det}. Section
\ref{sec:systematics} is dedicated to the impact of systematic effects
such as mismodeling the underlying physics or detector acceptance
effects. Numerical studies for one uni-angular and one triple-angular
distribution are provided in section \ref{sec:numerics}. In a series
of appendices we provide the orthonormal bases of angular functions
relevant to several rare $b$ decays.

@@

The orthonormality relations \refeq{def-ortho-rel} imply that a single angular observable $P_i$
can be projected out of the full PDF $P$ by means of
\begin{equation}
    \label{eq:det-Pi-analytical}
    P_i(\nuvec) = \int_{\thvec = 0}^{2\pi} f_i(\thvec) P(\nuvec, \thvec) \dd^n \theta\,.
\end{equation}
In point of fact, $P_i$ is the $f_i$-th moment of the PDF $P$\fred{This
  notation is uncommon. Is that how we \emph{define} the $f_i$-th
  moment?}. Additionally, integration over the non-angular variables
yields
\begin{equation}
    \langle P_i\rangle
    \equiv \int P_i(\nuvec) \dd^m \nu
    = \int \left[\int_{\thvec=0}^{2\pi} f_i(\thvec) P(\nuvec,\thvec) \dd^n\theta\right]\dd^m \nu\,.
\end{equation}
The remainder of this section  describes the method of moments, in which we replace the
analytical integration \refeq{det-Pi-analytical} by Monte Carlo (MC) estimators.\\

The central tenet of MC integration is the fact that the expectation value $E_P[g]$ of some function
$g(x)$ under the probability density $P(x)$,
\begin{equation}
    E_P[g] \equiv \int g(x) P(x) \dd x
\end{equation}
can be approximated \citeneeded\fred{Robert, Casella} by an MC estimator $\what{E_P[g]}$
\begin{equation}
    \label{eq:mc-id}
    E_P[g] \to \widehat{E_P[g]} \equiv \frac{1}{N} \sum_{k=1} g(x^{(k)})
\end{equation}
due to the strong law of large numbers for $N \to \infty$ assuming
that the variates $x^{(k)}$, $k = 1, \dots, N$ are distributed as
$P$; i.e.,
\begin{equation}
    x^{(k)} \sim P\,.
\end{equation}
Throughout this letter we denote all MC estimators with a wide hat.\\

We assume, for a moment, that $P$ describes the distribution of the underlying
physical process truthfully. In that case, all events detected in an experimental setup are in fact, up to
detection efficiencies, distributed as $P$. \fred{Paragraph is redundant an can be omitted.}

Application of \refeq{mc-id} then yields \fred{notation is very confusing $P_i$ for $x^{(k)} \sim P$}
\begin{equation}
    \langle P_i\rangle \to \widehat{\langle P_i\rangle} = \frac{1}{N} \sum_{k=1}^{N} f_i(x^{(k)})\,.
\end{equation}
It is often of interest to obtain the $\nuvec$- observables integrated
over certain ranges of $\nuvec$; i.e., binned measurements of $\langle
P_i\rangle$\footnote{% We refer for example to the determination of
  the angular observables $J_i$ in $\bar{B}\to\bar{K}^*\ell^+\ell^-$
  decays, see e.g. \cite{Aaij:2013iag}. For details on the relation
  between the $P_i$ and the angular observable $J_i$ in the
  aforementioned decay, we refer to appendix \ref{app:btokstarll}.  }.
Therefore, we introduce the bin-integrated quantity
\begin{align}
    \langle P_i\rangle_{\vec{a},\vec{b}}
    & = \int_{\vec{a}}^{\vec{b}} P_i(\nuvec) \dd^m \nu\\
    & = \int_{\vec{a}}^{\vec{b}} \left[\int_{\thvec=0}^{2\pi} f_i(\thvec) P(\nuvec,\thvec) \dd^n\theta\right]\dd^m \nu\\
    & = \int \left[\int_{\thvec=0}^{2\pi} f_i(\thvec) P(\nuvec,\thvec)
        \mathbf{1}(\vec{a} \le \nuvec \le \vec{b})\,
        %% \theta^{(m)}(\nuvec - \vec{a}) \theta^{(m)}(\vec{b} - \nuvec)
        \dd^n\theta\right]\dd^m \nu\,,
\end{align}
where the argument of the indicator function $ \mathbf{1}(\vec{a} \le
\nuvec \le \vec{b})$ is to be interpreted componentwise.
Application of \refeq{mc-id} immediately yields
\begin{equation}
    \label{bin-importance}
    \widehat{\langle P_i\rangle_{\vec{a},\vec{b}}}
    = \frac{1}{N} \sum_{k=1}^{N} f_i(x^{(k)})         \mathbf{1}(\vec{a} \le \nuvec \le \vec{b})\,.
\end{equation}
This basically reduces the estimation of
$\aver{P_i}_{\vec{a},\vec{b}}$ to a (weighted) counting experiment. In
the limit $N \to \infty$, the random vector $( \dots,
\aver{P_i}_{\vec{a},\vec{b}}, \dots)$ follows a multivariate Gaussian
distribution \citeneeded\fred{Why?  multivariate in $\widehat{P_i}$?}
with a mean vector estimated by \refeq{bin-importance} and covariance
estimated as
\begin{equation}
    \cov[\aver{P_i},\aver{P_j}]_{\vec{a},\vec{b}} \to \what{\cov}[\aver{P}_i, \aver{P}_j]_{\vec{a},\vec{b}}
        = \frac{1}{N - 1} \sum_{k=1}^{N} \big[{f}_i(x^{(k)}) - \widehat{\langle P_i\rangle_{\vec{a},\vec{b}}}\big]\,\big[f_j(x^{(k)}) - \widehat{\langle P_j\rangle_{\vec{a},\vec{b}}}\big]
        \mathbf{1}(\vec{a} \le \nuvec \le \vec{b})\,.
\end{equation}
We would like to emphasize that the sample covariance should rapidly \fred{So what value of $N$ is close enought to $\infty$?} converge towards the true covariance matrix.
This will allow to construct constraints on optimized observables with correlated uncertainties
from the experimental constraints on the angular observables. (See \cite{Egede:2008uy,Egede:2010zc,Bobeth:2010wg,Becirevic:2011bp,Bobeth:2012vn,Matias:2012xw,DescotesGenon:2012zf}
for definitions of such optimized observables in $B\to K^*\ell^+\ell^-$ decays).

@@

In \refsec{sample-based-det}, we assume that the PDF $P$ describe the physical reality accurately,
and that the experiment observes each event with perfect accuracy. In order to estimate systematic
uncertainties, we lift these assumptions.

\subsection{Mismodeling due to Contributions by Higher Partial Waves}
\label{sec:systematics:partial-waves}

\fred{Paragraph is very specific to one physics case. Needs a drawing}

@@

\fred{If this is to be general, should explain what we mean by
  acceptance. Isn't it that experiments just model the detector well?
  The P. to observe an event in $\nuvec, \thvec$ might be very
  different from the P. to create an event in $\nuvec, \thvec$. All
  that's needed is a full forward model. I'm not sure that in
  \refeq{eq:PDFwithDE} we still have a normalized probability. Am I
  right to say that detector effects can be very much localized and
  nondifferentiable? Like some wires are inactive, or the region close
  to the beam has zero acceptance. In the latter case, modeling
  residual acceptance effects with smooth Legendre polynomials seems a
  bad idea.}

Thanks to accurate detector simulations and control studies, the experimental analyses have become
remarkably good at removing detector acceptance effects. In this section we therefore assume that
there are only a small, residual acceptance effects left that affect the events. In particular, we
assume that the latter can be modeled as a modified probability density,
\begin{equation}
    \label{eq:PDFwithDE}
    P(\nuvec,\thvec) \to P(\nuvec,\thvec) \times \Omega(\thvec),
\end{equation}
where $\Omega$ is independent of the non-angular kinematics $\nuvec$. The latter assumption is only
is invalid in general. However, if residual angular acceptance only weakly depends on $\vec{\nu}$, one
can always choose appropriate bin $\vec{\nu}$ so that $\Omega$ is approximately constant with respect
to $\vec{\nu}$. For such a case we parametrize
\begin{equation}
    \Omega_{m,l}(\thvec) = \prod_{i=1}^{m} \Big[1 + \sum_{j=1}^l \eps_i^{(j)} p_j(\cos\theta_i)\big]
\end{equation}
where $p_j(\cos\theta_i)$ denotes the $j$th Legendre polynomial. Since we only consider residual
acceptance effects, we expect $\eps_i^{(j)} \ll 1$. \footnote{\danny{what are reasonable values/upper limits on the $\eps$?}}\\

@@

\todo{
\begin{itemize}
    \item Simulate this for one angle $\theta_{1}$ (similar to $B\to K \ell^+\ell^-$) with varying samples sizes.
    \item Simulate this for three angles $\theta_{1\dots 3}$ (similar to $B\to K^*(\to K \pi)\ell^+\ell^-$) with varying samples sizes.
    \item Also, check explicitly the variance and covariance of the results for all sample sizes considered.
    \item compare robustness to likelihood fit when fit doesn't
      converge. Why exactly doesn't it converge? What if physics model
      wrong, say some angular terms are missing.
\end{itemize}}

@@

In this letter \dots
\begin{enumerate}
    \item errors on the means are in very good approximation gaussian.
    \item correlation are small and faithfully model a multivariate gaussian. \fred{$\Rightarrow$ easy transfer of knowledge to theory fits}
\end{enumerate}

@@

The PDF for the decay $\bar{B}\to\bar{K}\ell^+\ell^-$ has been calculated for the most
complete basis of dimension-six $b\to s \ell^+\ell^-$ operators. It reads \cite{Bobeth:2007dw,Bobeth:2012vn}
\begin{equation}
    P(q^2, \cos\theta_1) = \frac{1}{\Gamma} \frac{\dd^4\Gamma}{\dd q^2\,\dd \cos\theta_1} = \frac{a(q^2)}{\Gamma} + \frac{b(q^2)}{\Gamma} \cos\theta_1 + \frac{c(q^2)}{\Gamma} \cos^2\theta_1 = \sum_i P_i f_i(\cos\theta_1)\,,
\end{equation}
where the basis of angular functions $f_i$ reads
\begin{equation}
\begin{aligned}
    f_1 & = 1\,, &
    f_2 & = \cos\theta_1\,, &
    f_2 & = \cos^2\theta_1\,.
\end{aligned}
\end{equation}
Here we denote the dilepton mass squared as $q^2$, and the dilepton helicity angle as $\theta_1 \equiv \theta_{\ell}$. We transform the PDF from a $\cos\theta_1$-dependence
to a $\theta_1$-dependence \fred{why? Formula easier? Where is the ``-'' sign from the Jacobian $\partial_{\theta} \cos \theta = - \sin \theta$ },
\begin{equation}
    P(q^2, \theta_1) = \sum_i P_i f_i(\cos\theta_1) \sin \theta_1\,.
\end{equation}

We provide dual basis $\hat{f}_i$ of angular functions which is dual to the basis $f_i$ in the sense that \fred{What are the upper limits? $\pi$ or $2 \pi$? Not consistent with section I and II. I think it would be fair to talk about the dual basis already there.}
\begin{equation}
    \int_0^\pi \dd\theta_1 \hat{f}_i(\theta_1) f_j(\theta_1) \sin\theta_1 = \delta_{ij}\,,
\end{equation}
thereby enabling us to project out exactly one of the angular
observables $P_i(q^2)$
\begin{equation}
    \int_0^\pi \dd \theta_1\hat{f}_i(\theta_1) P(q^2, \theta_1) = P_i(q^2)\,.
\end{equation}
The dual basis reads
\begin{equation}
\begin{aligned}
    \hat{f}_1 & = \frac{9}{8} - \frac{15}{8}\cos^2\theta_1\,, &
    \hat{f}_2 & = \frac{3}{2}\cos\theta_1\,, &
    \hat{f}_3 & = -\frac{15}{8} + \frac{45}{8}\cos^2\theta_1\,.
\end{aligned}
\end{equation}
